|

### 2021-08-09 appendix/appendix.Rmd
lemma bargaining

\begin{lemma}
The amount of rents required to win support from a given legislator decreases when the number of legislators increase.
\end{lemma}

@@

\[
\begin{aligned}
b(N+1) - b(N) \ = \ & \dfrac{1}{2(N+1)+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-(N+1)(\underline{t} + B) + B\right] \\
& - \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
= \ & XXXX \\
= \ & XXXX \\
< \ &0
\end{aligned}
\]

>>>>

\begin{lemma}\label{lemmabarg}
The amount of rents required to win support from a given legislator decreases when the number of legislators increase.
\end{lemma}

@@

\[
\begin{aligned}
b(N+1) - b(N) \ = \ & \dfrac{1}{2(N+1)+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-(N+1)(\underline{t} + B) + B\right] \\
& - \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
= \ & \dfrac{1}{2N+1}\left[\left(1-\dfrac{2}{2N+3}\right)\left(2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-N(\underline{t} + B) + \underline{t}\right) \right. \\
& - \left. 2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
= \ & -\dfrac{1}{2N+1}\left[\dfrac{2}{2N+3}\left(2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-N(\underline{t} + B) + \underline{t}\right) \right. \\
& + \left. \dfrac{2 R \delta (1-\delta)}{2N} + \underline{t} + B\right] \equiv \Delta b(N) \\
< \ &0
\end{aligned}
\]

Therefore, larger legislature sizes decrease the costs of bargaining. This because of two effects: first, the chance of being the proposer decreases; second, the chance of being selected to receive an offer also decreases.
